Do moral communities have a spatial dimension? A spatial exploratory analysis of places of worship and violent crime in the city of Recife, Brazil

### 2019-10-14 Moral_Communities_and_Crime_v1.tex
Completed first draft of methods and started working on the sections on context/data and analysis and results. Changed the name of the RData file to Moral_Communities_Crime_Recife.RData

The preceding review makes clear the need for research at various
geographical scales. From a theoretical perspective, the social
mechanisms that underpin the hypothesis of moral communities and
informal social control can happen at various geographical scales, some
of which previous research has already addressed: the work of Nie and
Yang (2019), for one, highlights the role of processes detectable at a
relatively high level of aggregation, whereas Warner and Konkel (2019),
looking specifically at the effect of places of worship, bring the study
closer to the level of the neighborhood. In what follows, we propose to
adopt a much more disaggregated approach by considering the intensity of
criminal events with respect to places of worship. This requires
micro-level data both of crimes and places of worship, and the use of
appropriate spatial analytical tools for point patterns, as discussed
next.

@@

Two different techniques are deployed in this paper to study the spatial
distribution of criminal events, and their possible relationship to the
location of places of worship. Firstly, the F-function is a nearest
neighbor technique that is used to summarize the distance between a set
of points and their nearest events. This technique has found extensive
use in spatial epidemiology (see Gatrell et al., 1996) and has also been
used in spatial criminology (see, inter alia, Craglia et al., 2000;
Kiani et al., 2015; Levine, 2006; and Rogerson and Sun, 2001). The
second technique is the scan statistic. This method has also been
extensively used in spatial epidemiology (e.g., Hjalmars et al., 1996)
and has found use in spatial criminology as well (see He et al., 2017a;
Nakaya and Yano, 2010; Malleson and Andresen, 2015; and Shiode, 2011).
Use of these two techniques is meant to provide insights with respect to
1) the location of violent criminal events with respect to various types
of facilities; and 2) geographically identify places of worship
associated with clusters of criminal events. These two techniques are
briefly reviewed next.

\hypertarget{quadrat-analysis}{%
\subsection{Quadrat Analysis}\label{quadrat-analysis}}

Words go here.

\hypertarget{relative-intensity}{%
\subsection{Relative Intensity}\label{relative-intensity}}

Words go here.

\hypertarget{case}{%
\section{Case Study}\label{case}}

\hypertarget{context}{%
\subsection{Context}\label{context}}

The study is of the city of Recife, the capital of the state of
Pernambuco in the Northeast region of Brazil. With a population of
1,550,390 million inhabitants in 2010, and with an area of 7,133.2 km2,
Recife is one of the main Brazilian metropolises, exerting a great
economic influence in neighboring regions. However, the city experiences
a serious problem with violent crime, and has the dubious honor of being
one of the five capital cities in Brazil with the highest homicide rates
in the period under study (Menezes et al. 2013).

In the current context, the term ``violent crime'' is an umbrella for
several forms of infractions to the penal code. Following
recommendations of the National Secretariat of Public Security of the
Ministry of Justice of 2006, these are Violent Lethal and Intentional
Crimes (VLIC; which includes intentional homicide), theft followed by
death (robbery), and corporal injury followed by death. The data on CVLI
were extracted from the Police Information System of the Secretariat of
Social Defense of Pernambuco (INFOPOL / SDS-PE), which is the most
reliable, detailed, and comprehensive information on violent deaths in
the region.

@@

\caption{\label{tab:descriptive-statistics}\label{tab:descriptive-statistics}Characteristics of Violent Crime in Recife, July, 2008 - June, 2009}
\centering
\begin{tabular}[t]{lr}
\toprule
 & Percentage\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Gender of Victim}}\\
\hspace{1em}Man & 91.35\\
\hspace{1em}Woman & 8.65\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Type of Crime}}\\
\hspace{1em}Murder & 97.82\\
\hspace{1em}Robbery & 2.00\\
\hspace{1em}Body injury followed by death & 0.18\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Ethnicity of Victim}}\\
\hspace{1em}Black and White & 95.11\\
\hspace{1em}Yellow and White & 1.27\\
\hspace{1em}Not Reported & 3.62\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Age of Victim}}\\
\hspace{1em}1 to 12 years & 0.18\\
\hspace{1em}13 to 17 years & 11.31\\
\hspace{1em}18 to 30 years & 61.70\\
\hspace{1em}31 to 65 years & 25.84\\
\hspace{1em}65 years and older & 0.73\\
\hspace{1em}Not Reported & 0.24\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Weapon Used}}\\
\hspace{1em}Firearm & 87.51\\
\hspace{1em}Other & 12.49\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{data}{%
\subsection{Data}\label{data}}

The data are organized at the individual level and it is possible to
obtain information about the location, day of the week, day of the
month, period of the day, as well as gender, age, and race of the
victim. The database used in this study comprises the period from July
1, 2008 to June 30, 2010. Some descriptive statistics regarding this
dataset are reported in Table 1, where it can be seen that overall,
about 91\% of the victims of CVLI in the period analyzed were men, while
approximately 98\% of violent crimes were homicides. In addition, most
of the victims were black or brown, and the youth population between the
ages of 18 and 30 is the most affected by violent crime. Lastly, it
should be noted that about 88\% of the criminal events under analysis
involved firearms. Information about places of interest was obtained
from the National Register of Addresses for Statistical Purposes (CNEFE
- Census 2010), which lists 78,056,411 urban and rural addresses,
distributed among the 316,574 census tracts. This is the first database
of its kind produced by IBGE, and the first version was produced at the
time of the 2000 Census. The way addresses are described in the National
Register is very rich, and it is possible to identify the names of the
places of worship including their denomination. Georeferencing was used
to geolocate each place of worship. In this way, a total of 1,719 places
of worship were geolocated in the city of Recife. Figure 1 (Panel a)
shows the spatial distribution of the 1,657 CVLI crimes that occurred in
the city of Recife between 2008.2 and 2010.1. Panel b) of the figure
shows the spatial distribution of places of worship in the region.

@@

\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/plot-crime-1} \hfill{}

\caption{\label{fig:plot-crime}Lethal and Intentional Violent Crime in Recife}\label{fig:plot-crime}
\end{figure}

@@

\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/plot-events-1} \hfill{}

\caption{\label{fig:plot-events}Places of Worship and Commercial Establishments in Recife}\label{fig:plot-events}
\end{figure}

\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/plot-sed-1} \hfill{}

\caption{\label{fig:plot-sed}Socio-Economic Deprivation in Recife}\label{fig:plot-sed}
\end{figure}

@@

\hypertarget{quadrat-analysis-1}{%
\subsection{Quadrat Analysis}\label{quadrat-analysis-1}}

\begin{figure}
\centering
\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/plot-sed-as-quintiles-1.pdf}
\caption{\label{fig:plot-sed-as-quintiles}Socio-Economic Deprivation as
Quintiles}
\end{figure}

@@

\hypertarget{relative-intensity-1}{%
\subsection{Relative Intensity}\label{relative-intensity-1}}

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

The preceding review, as well as other research (2019), makes clear the
need for research at various geographical scales. From a theoretical
perspective, the social mechanisms that underpin the hypothesis of moral
communities and informal social control can happen at various
geographical scales, some of which previous research has already
addressed: the work of Nie and Yang (2019), for one, highlights the role
of processes detectable at a relatively high level of aggregation,
whereas Warner and Konkel (2019), looking specifically at the effect of
places of worship, bring the study closer to the level of the
neighborhood. In what follows, we propose to adopt a much more
disaggregated approach by considering the intensity of criminal events
with respect to places of worship. This requires micro-level data both
of crimes and places of worship, and the use of appropriate spatial
analytical tools for point patterns, as discussed next.

@@

As noted above, previous research that has investigated the presence of
churches from a geographical perspective has used data aggregated at
different scales. In the case of Nie and Yang (2019), the unit of
analysis was the county, whereas Warner and Konkel (2019) used Census
Block Groups, a much smaller unit of analysis. Research in spatial
criminology, on the other hand, has studied criminal events as point
patterns since at least the work of Levine et al.~(1986) investigated
the concentration of criminal events in the proximity of bus stops.
Since then, many other works have applied tools of spatial point pattern
analysis to investigate the empirical properties of the distribution of
crime. This includes Craglia et al.~(2000) who used the Ripley's
K-function (Ripley 1976) to investigate clustering processes, and
Rogerson and Sun (2001) who applied nearest neighbor techniques to the
study of arson. More recent studies of crime as point patterns are
Nakaya and Yano (2010), Kiani et al.~(2015), and Malleson and Andresen
(2015).

Readers interested in point pattern analysis techniques are urged to
consult the still valuable Bailey and Gatrell (1995) or for an
up-to-date and in-depth coverage of the topic, the excellent text by
Baddeley et al.~(2015). In this paper we will concentrate on one
property of point processes, namely the intensity. Suppose that the
outcome of interest is the number of events per unit area
\(Y(\mathcal{A})\). This could be, for instance, the number of criminal
events observed in an arbitrary area. The intensity of a point pattern
then is as follows: \[
\lambda(s)=\lim_{\text{d}s \to 0}\frac{E[Y(\text{d}s)]}{\text{d}s}
\]

where \(\lambda(s)\) is the intensity of the process at point \(s\),
given by the expected number of events in a small area \(\text{d}s\)
around \(s\), as the area becomes arbitrarily small. If the process is
homogeneous (i.e., the intensity is a constant over space), an apt
estimator of the intensity is the global intensity, simply the number of
events divided by the area of the region under analysis: \[
\hat{\lambda} = \frac{n}{|\mathcal{A}|}
\]

When the process is not homogeneous, other estimators are more
appropriate. In the analysis to follow we use two estimators of
intensity: conditional quadrat counts and relative distribution
estimate. These techniques are briefly discussed next.

\hypertarget{conditional-quadrat-counts}{%
\subsection{Conditional Quadrat
Counts}\label{conditional-quadrat-counts}}

Quadrat counts is a relatively simple technique to analyze spatial
variations in the intensity of a point process. It operates by
partitioning the region under study \(\mathcal{A}\) into subregions
\(\mathcal{A}_1,\cdots,\mathcal{A}_m\). These subregions are mutually
exclusive, and their union is identical to \(\mathcal{A}\). In the
simplest case, the subregions have equal area. The number of events
within each subregion (i.e., \(n_{\mathcal{A}}\)) divided by the area of
the subregion (i.e., \(|\mathcal{A}|\)) is a local estimate of the
intensity: \[
\lambda(\mathcal{A}_i)=\frac{n_{\mathcal{A}_i}}{|\mathcal{A}_i|}
\]

A test for homogeneity consists of assessing whether the intensity of
the point process at the quadrats is uniform: \[
\lambda(\mathcal{A}_1)=\cdots=\lambda(\mathcal{A}_m)
\]

Using quadrats of equal size is a convenient simplication, but in
principle the areas could be different - in which case the count of
events would be proportional to the area of the quadrat under
homogeneity. An interesting variation of this technique is conditional
quadrat counts, whereby the partition of regions
\(\mathcal{A}_1,\cdots,\mathcal{A}_m\) is done to reflect an underlying
covariate of interest, say \(Z\). By introducing a covariate as a
partitioning criterion, it becomes possible to calculate estimators of
the intensity of quadrats at different levels of the value of the
covariate. For exploratory purposes, we can plot average intensity by
quadrat, and compare to the global intensity.

\hypertarget{relative-distribution-estimate}{%
\subsection{Relative Distribution
Estimate}\label{relative-distribution-estimate}}

Conditional quadrat counts allow us to explore whether the intensity of
the process depends on a covariate \(Z\). A different way of expressing
this is as follows: \[
\lambda(s)=\rho\big(Z(s)\big)
\]

In this case, the intensity is a function \(\rho\) that maps how the
intensity depends on covariate \(Z\). Non-parametric estimation of
\(\rho\) uses the ratio of the density of covariate values at the
locations of the point process, relative to the \emph{spatial
distribution function} \(G\), the density of covariate values at random
locations (see Baddeley, Rubak, and Turner 2015, 179).

The density of covariate values at the locations of the is obtained by
means of a kernel density estimator, for example: \[
\lambda_0(s) = \frac{1}{|\mathcal{A}|}\sum_{i = 1}^n\kappa(Z(s_i) - z)
\] where \(s_i\) are the locations of the points.

On the other hand, \(G\) which is the cumulative distribution function
of \(Z\) at random point \(S\) uniformly distributed in \(\mathcal{A}\)
: \[
G(z) = \frac{1}{|\mathcal{A}|} \int_{\mathcal{A}}\text{I}\{Z(s)\leq z\}\text{d}s
\] where \(\text{I}\) is an indicator function that takes the value of
\(1\) if the argument is true, and the value of \(0\) otherwise. In
practice, the spatial distribution function is approximated based on a
discretization of space using a fine grid of pixels as follows: \[
G(z) = \frac{\#\{\text{pixels }s:Z(s)\leq z\}}{\# \text{pixels}}
\]

Therefore, an estimator of \(\rho\) is as follows: \[
\rho(z) = \frac{1}{|\mathcal{A}|G'(z)}\sum_{i=1}^n\kappa(Z(s_i) - z)
\] where the derivative \(G'\) can be approximated by differentiating a
smoothed estimated of \(G\). Other estimators are discussed by Baddeley
et al.~(Baddeley, Rubak, and Turner 2015, 180).

It is possible to adjust the relative distribution estimate by means of
a baseline; a baseline in this case can be a function of other
covariates that might confound the estimates of the relative
distribution, so that the relative intensity \(\lambda(s)/B(s)\) can be
assumed to depend only on covariate \(Z\). Therefore: \[
\lambda(s) = \rho(Z(s))B(s)
\] where \(B(s)\) is a baseline function. It can be seen that
\(\rho(z)=1\) is the baseline intensity; values of \(\rho(z)>1\)
correspond to intensities higher than the baseline \emph{as a function
of} \(Z(u)\), whereas values of \(\rho(z)<1\) correspond to intensities
lower than the baseline, again as a function of \(Z(u)\).

\hypertarget{case}{%
\section{Case Study: Context and Data}\label{case}}

The study is of the city of Recife, the capital of the state of
Pernambuco in the Northeast region of Brazil. With a population of
1,550,390 million inhabitants in 2010, Recife is one of the main
Brazilian metropolises, exerting a great economic influence in
neighboring regions. However, the city experiences a serious problem
with violent crime, and has the dubious honor of being one of the five
capital cities in Brazil with the highest homicide rates in the period
under study (Menezes et al. 2013).

In the current context, the term ``violent crime'' is an umbrella for
several forms of infractions to the penal code. Following
recommendations of the National Secretariat of Public Security of the
Ministry of Justice of 2006, these are Violent Lethal and Intentional
Crimes (VLIC; which includes intentional homicide), theft followed by
death (robbery), and corporal injury followed by death. The data on LIVC
were extracted from the Police Information System of the Secretariat of
Social Defense of Pernambuco (INFOPOL / SDS-PE), which is the most
reliable, detailed, and comprehensive information on violent deaths in
the region.

@@

\caption{\label{tab:table-descriptive-statistics}\label{tab:descriptive-statistics}Characteristics of Violent Crime in Recife, July, 2008 - June, 2009}
\centering
\begin{tabular}[t]{lr}
\toprule
 & Percentage\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Gender of Victim}}\\
\hspace{1em}Man & 91.35\\
\hspace{1em}Woman & 8.65\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Type of Crime}}\\
\hspace{1em}Murder & 97.82\\
\hspace{1em}Robbery & 2.00\\
\hspace{1em}Body injury followed by death & 0.18\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Ethnicity of Victim}}\\
\hspace{1em}Black and White & 95.11\\
\hspace{1em}Yellow and White & 1.27\\
\hspace{1em}Not Reported & 3.62\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Age of Victim}}\\
\hspace{1em}1 to 12 years & 0.18\\
\hspace{1em}13 to 17 years & 11.31\\
\hspace{1em}18 to 30 years & 61.70\\
\hspace{1em}31 to 65 years & 25.84\\
\hspace{1em}65 years and older & 0.73\\
\hspace{1em}Not Reported & 0.24\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Weapon Used}}\\
\hspace{1em}Firearm & 87.51\\
\hspace{1em}Other & 12.49\\
\bottomrule
\end{tabular}
\end{table}

The data are organized at the individual level and it is possible to
obtain information about the location, day of the week, day of the
month, period of the day, as well as gender, age, and race of the
victim. The database used in this study comprises the period from July
1, 2008 to June 30, 2010. Some descriptive statistics regarding this
dataset are reported in Table 1, where it can be seen that overall,
about 91\% of the victims of LIVC in the period analyzed were men, while
approximately 98\% of violent crimes were homicides. In addition, most
of the victims were black or brown, and the youth population between the
ages of 18 and 30 is the most affected by violent crime. Lastly, it
should be noted that about 88\% of the criminal events under analysis
involved firearms. Figure \ref{fig:plot-crime} shows the spatial
distribution of the 1,657 LIVC crimes that occurred in the city of
Recife between July, 2008 and June, 2010.

@@

\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/fig-plot-crime-1} \hfill{}

\caption{\label{fig:plot-crime}Location of Lethal and Intentional Violent Crime in Recife, July, 2008 - June, 2009}\label{fig:fig-plot-crime}
\end{figure}

Information about places of interest was obtained from the National
Register of Addresses for Statistical Purposes (CNEFE - Census 2010),
which lists 78,056,411 urban and rural addresses, distributed among the
316,574 census tracts. This is the first database of its kind produced
by IBGE, and the first version was produced at the time of the 2000
Census. The way addresses are described in the National Register is very
rich, and it is possible to identify the names of the places of worship
including their denomination. Georeferencing was used to geolocate each
place of worship. In this way, a total of 1,719 places of worship were
geolocated in the city of Recife.

@@

\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/fig-plot-events-1} \hfill{}

\caption{\label{fig:plot-events}Location of Places of Worship and Commercial Establishments in Recife}\label{fig:fig-plot-events}
\end{figure}

@@

The analysis is implemented using the \texttt{R} statistical computing
language, and documents to replicate the analysis, in addition to all
data necessary, can be obtained from this anonymous shared folder:

\url{https://drive.google.com/open?id=1tuJM4Mhi0Ftq3ZEwjv6RP9vO3veGjIR_}

\hypertarget{socio-economic-deprivation}{%
\subsection{Socio-Economic
Deprivation}\label{socio-economic-deprivation}}

The first step in our analysis is to obtain an indicator of
Socio-Economic Deprivation (SED). Socio-economic deprivation is known to
correlated positively with crime, as it often reflects relevant
criminogenic factors such as poverty and family disruption (He et al.
2015). In the present case, we have for the city of Recife information
about the variables shown in Table \ref{tab:sed-descriptive-statistics}
at the level of \emph{setores}, a small Brazilian census geography.

As seen in the table, Recife is a city with large socio-economic and
demographic disparities; for example, the \emph{setor} with the highest
median income has a median income that is 6,517\% higher than the median
income in the \emph{setor} with the lowest median income. Whereas there
are \emph{setores} where the proportion of population who are unemployed
is zero, there are \emph{setores} where almost 60\% of the population
are unemployed. Likewise, there are \emph{setores} where almost 70\% of
the population lives in poverty. In addition to these economic
indicators, two variables are used to represent family disruption, the
proportion of families whose head is a single mother, and the proportion
of families whose head is a \emph{young} single mother, that is, a woman
between the ages of 15 and 25. As can be seen, there are \emph{setores}
with approximately 70\% of households led by single mothers, and of
these, over 21\% are led by younger women, indicating a high degree of
family disruption.

For the analysis, we use Principal Component Analysis, a data reduction
technique, to obtain an indicator of Socio-Economic Deprivation. The
loadings of the first factor, which accounts for almost 54\% of the
variance, are shown in Table \ref{tab:sed-descriptive-statistics}. The
loadings of this factor indicate that high Socio-Economic Deprivation is
a combination of (in terms of importance): high levels of poverty, high
levels of unemployment, and low median income, followed by high levels
of family disruption, in particular proportion of families led by young
single mothers.

\caption{\label{tab:table-sed-descriptive-statistics}\label{tab:sed-descriptive-statistics}Descriptive statistics of some key socio-economic and demographic variables in Recife}
\centering
\begin{tabular}[t]{lrrrrrrr}
\toprule
Variable & Min & 2nd Quartile & Median & Mean & 3rd Quartile & Max & \makecell[l]{PC Factor 1\\ Loadings}\\
\midrule
Median Income & 122.05 & 337.40 & 581.67 & 1031.09 & 1283.79 & 7954.19 & -0.42\\
Proportion Unemployed & 0.00 & 0.05 & 0.10 & 0.10 & 0.14 & 0.59 & 0.56\\
Proportion Poverty & 0.00 & 0.05 & 0.11 & 0.12 & 0.17 & 0.63 & 0.58\\
Proportion Single Mother & 0.00 & 0.33 & 0.37 & 0.37 & 0.41 & 0.70 & 0.17\\
Proportion Young Single Mother & 0.00 & 0.01 & 0.02 & 0.02 & 0.02 & 0.21 & 0.38\\
\bottomrule
\multicolumn{8}{l}{\textit{Note: }}\\
\multicolumn{8}{l}{The variable for young single mothers is for women aged 15-25}\\
\multicolumn{8}{l}{The first principal component accounts for 53.91\% of the variance}\\
\end{tabular}
\end{table}

Figure \ref{fig:plot-sed-as-quintiles} displays the geography of
Socio-Economic Deprivation in Recife, after classifying \emph{setores}
by quintiles, whereby the ``High'' class corresponds to \emph{setores}
in the top 20\% of the Socio-Economic Deprivation indicator, and the
``Low'' class corresponds to \emph{setores} in the bottom 20\% of the
Socio-Economic Deprivation indicator. The figure shows a veritable
mosaic of affluence and deprivation, with high deprivation areas
directly in contact, and in some cases even completely surrounded, by
low deprivation areas. This geographical pattern of unequality, on the
other hand, seems to be characteristic of Brazilian metropolitan
regions, where enclaves of wealth and \emph{favelas} (i.e., urban slums)
can be found in close proximity (see for example Feitosa et al. 2007).

\begin{figure}
\centering
\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/plot-sed-as-quintiles-1.pdf}
\caption{\label{fig:plot-sed-as-quintiles}Socio-Economic Deprivation in
Recife classified by quintiles}
\end{figure}

\hypertarget{conditional-quadrat-analysis}{%
\subsection{Conditional Quadrat
Analysis}\label{conditional-quadrat-analysis}}

@@

\hypertarget{relative-distribution}{%
\subsection{Relative Distribution}\label{relative-distribution}}

\hypertarget{relative-distribution-with-a-baseline-function}{%
\subsection{Relative Distribution with a Baseline
Function}\label{relative-distribution-with-a-baseline-function}}

@@

\leavevmode\hypertarget{ref-Baddeley2015spatial}{}%
Baddeley, Adrian, Ege Rubak, and Rolf Turner. 2015. \emph{Spatial Point
Patterns: Methodology and Applications with R}. Book. Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Bailey1995interactive}{}%
Bailey, T. C., and A. C. Gatrell. 1995. \emph{Interactive Spatial Data
Analysis}. Book. Essex: Addison Wesley Longman.

@@

\leavevmode\hypertarget{ref-Craglia2000comparative}{}%
Craglia, M., R. Haining, and P. Wiles. 2000. ``A Comparative Evaluation
of Approaches to Urban Crime Pattern Analysis.'' Journal Article.
\emph{Urban Studies} 37 (4): 711--29. \url{ISI:000086520800005}.

@@

\leavevmode\hypertarget{ref-Feitosa2007global}{}%
Feitosa, F. F., G. Camara, A. M. V. Monteiro, T. Koschitzki, and M. P.
S. Silva. 2007. ``Global and Local Spatial Indices of Urban
Segregation.'' Journal Article. \emph{International Journal of
Geographical Information Science} 21 (3): 299--323.
\href{ISI:000244944300004\%0AC:/Papers/International\%20Journal\%20of\%20Geographical\%20Information\%20Science/IJGIS\%20(2007)\%2021\%20(3)\%20299-323.pdf}{ISI:000244944300004
C:/Papers/International Journal of Geographical Information Science/IJGIS (2007) 21 (3) 299-323.pdf}.

@@

\leavevmode\hypertarget{ref-He2015temporal}{}%
He, L., A. Paez, D. S. Liu, and S. G. Jiang. 2015. ``Temporal Stability
of Model Parameters in Crime Rate Analysis: An Empirical Examination.''
Journal Article. \emph{Applied Geography} 58: 141--52.
\url{https://doi.org/10.1016/j.apgeog.2015.02.002}.

@@

\leavevmode\hypertarget{ref-Kiani2015analysis}{}%
Kiani, Rasoul, Siamak Mahdavi, and Amin Keshavarzi. 2015. ``Analysis and
Prediction of Crimes by Clustering and Classification.''
\emph{International Journal of Advanced Research in Artificial
Intelligence} 4 (8): 11--17.

@@

\leavevmode\hypertarget{ref-Levine1986crime}{}%
Levine, Ned, Martin Wachs, and Elham Shirazi. 1986. ``Crime at Bus
Stops: A Study of Environmental Factors.'' \emph{Journal of
Architectural and Planning Research}, 339--61.

@@

\leavevmode\hypertarget{ref-Malleson2015spatio}{}%
Malleson, Nick, and Martin A Andresen. 2015. ``Spatio-Temporal Crime
Hotspots and the Ambient Population.'' \emph{Crime Science} 4 (1): 10.

\leavevmode\hypertarget{ref-Malleson2019identifying}{}%
Malleson, N., W. Steenbeek, and M. A. Andresen. 2019. ``Identifying the
Appropriate Spatial Resolution for the Analysis of Crime Patterns.''
Journal Article. \emph{Plos One} 14 (6).
\url{https://doi.org/10.1371/journal.pone.0218324}.

@@

\leavevmode\hypertarget{ref-Nakaya2010visualizing}{}%
Nakaya, T., and K. J. Yano. 2010. ``Visualising Crime Clusters in a
Space-Time Cube: An Exploratory Data-Analysis Approach Using Space-Time
Kernel Density Estimation and Scan Statistics.'' Journal Article.
\emph{Transactions in Gis} 14 (3): 223--39.
\url{https://doi.org/10.1111/j.1467-9671.2010.01194.x}.

@@

\leavevmode\hypertarget{ref-Ripley1976second}{}%
Ripley, B. D. 1976. ``The Second-Order Analysis of Stationary Point
Processes.'' Journal Article. \emph{Journal of Applied Probability} 13
(2): 255--66. \url{ISI:A1976CA37400007}.

\leavevmode\hypertarget{ref-Rogerson2001spatial}{}%
Rogerson, Peter, and Y Sun. 2001. ``Spatial Monitoring of Geographic
Patterns: An Application to Crime Analysis.'' \emph{Computers,
Environment and Urban Systems} 25 (6): 539--56.
